Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-01-27 paper/elsarticle/main.tex
paper:acknowledgements, nomenclature added and title changed

\title{Self-tunable approximated explicit MPC: Heat exchanger implementation}
%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}

@@

>>>>

\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys}
%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}

@@

\section*{Acknowledgements}
This research is funded by the European Union’s Horizon Europe under grant no. 101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries). The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, the Slovak Research and Development Agency under the project APVV-20-0261.

\section*{Nomenclature}

\subsection{Abbreviations}
\noindent  \textit{MPC}: model predictive control \\
\textit{ISE}: integral square error \\
\textit{LTI}: linear time-invariant \\

\subsection{Symbols}
\noindent $A$: system state matrix \\
$\widetilde{A}$: extended system state matrix \\
$B$: system input matrix \\
$\widetilde{B}$: extended system input matrix \\
$C$: system output matrix \\
$\widetilde{C}$: extended system output matrix \\
$d_{\max}$: maximal deviation from the steady state \\
TODO: odlisit max size of reference step change \\
$F$: slope of the affine control law \\
$g$: section of the affine control law \\
$I$: identity matrix \\	
$k$: step of the prediction horizon \\
$N$: prediction horizon \\
$n_{\mathrm{u}}$: size of system inputs \\
$n_{\mathrm{y}}$: size of system outputs \\
$n_{\widetilde{\mathrm{x}}}$: size of extended system states \\
$Q_{\mathrm{x}}$: penalty matrix of the built-in integrator \\
$Q_{\mathrm{x,L}}$: lower bound on the penalty matrix of the built-in integrator \\
$Q_{\mathrm{x,U}}$: upper bound on the penalty matrix of the built-in integrator \\
$Q_{\mathrm{y}}$: penalty matrix of the control error \\
$Q_{\mathrm{y,L}}$: lower bound on the penalty matrix of the control error \\
$Q_{\mathrm{y,U}}$: upper bound on the penalty matrix of the control error \\
$R$: penalty matrix of system inputs \\
$R_{\mathrm{L}}$: lower bound on the penalty matrix of system inputs \\
$R_{\mathrm{U}}$: upper bound on the penalty matrix of system inputs \\
$\mathcal{R}$: critical region \\
$\mathbb{R}$: Euclidean space of real numbers \\
$t$: time, s \\
$t_{\epsilon}$: settling time, s \\
$T$: temperature, $^{\circ}\mathrm{C}$ \\
$T_{\mathrm{s}}$: sampling time, s \\
$T^{\mathrm{s}}$: steady state of temperature, $^{\circ}\mathrm{C}$ \\
$u$: control inputs \\
$u_{\mathrm{L}}$: control inputs asscociated with the lower boundary controller\\
$u_{\mathrm{U}}$: control inputs asscociated with the upper boundary controller\\
$U$: voltage, \% \\
$U^{\mathrm{s}}$: steady state of voltage, \% \\
$\mathcal{U}$: set of control inputs \\
$V$: volume of heating medium, l \\
$x$: system states \\
$\widetilde{x}$: extended system states \\
$x_{\mathrm{I}}$: system states corresponding to the built-in integrator \\
$y$: system outputs \\
$y_\mathrm{\max}$: maximal value of system outputs \\
$y_\mathrm{\min}$: minimal value of system outputs \\
$y_\mathrm{ref}$: reference value of system outputs \\	
$\mathcal{Y}$: set of system outputs \\
\textit{0}: zero matrix

\subsection{Greek letters}
\noindent $\Delta_\mathrm{ref}$: size of the reference change, $^{\circ}\mathrm{C}$ \\
$\rho$:	tuning factor \\
$\widetilde{\rho}$: scaled tuning factor \\
$\rho_{\mathrm{s}}$: splitting value of the tuning factor \\
$\sigma_{\max}$: maximal overshoot, \% \\
$\theta$: parameter of optimization problem \\
$\Theta$: set of parameter values
